\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-16 canonicitymodel.tex
Save. Fix comments.

Another helpful analogy of the canonicity model is that $"Tm"_p~\Gamma^C~"T"^C~"t"$ can be understood as $"t" \in \{$ Reducible Terms of type $T$ (and $T_p$) in context $\Gamma$ (and $\Gamma_p$) $\}$. The latter is more conventional and the former can be understood as type theoretic encoding of the latter\footnote{We usually use predicate to encode "belong to" relation in type theory}. From this perspective, this part of the canonicity model is quite similar to how conventional (proof-irrelevant) logical relation is carried out\citep{skorstengaard2019introduction} --
% cite https://arxiv.org/abs/1907.11133
using the terminology of the conventional formulation, $\Gamma_p$ will be the set of substitution into closed reducible terms, and we will prove $t[\gamma] \in T_p$, a set of closed reducible term of type $T$ when $\gamma \in \Gamma_p$.

>>>>

Another helpful analogy of the canonicity model is that $"Tm"_p~\Gamma^C~"T"^C~"t"$ can be understood as $"t" \in \{$ Reducible Terms of type $T$ (and $T_p$) in context $\Gamma$ (and $\Gamma_p$) $\}$. The latter is more conventional and the former can be understood as type theoretic encoding of the latter\footnote{We usually use predicate to encode "belong to" relation in type theory}. From this perspective, this part of the canonicity model is quite similar to how conventional (proof-irrelevant) logical relation is carried out\citep{skorstengaard2019introduction} --
using the terminology of the conventional formulation, $\Gamma_p$ will be the set of substitution into closed reducible terms, and we will prove $t[\gamma] \in T_p$, a set of closed reducible term of type $T$ when $\gamma \in \Gamma_p$.

### 2022-06-16 coq-example.tex
Save. Fix comments.

\subsection{Abstract Interpreters for Imp}
The second example is adapted and modified from the Familia\citep{zhang2017familia}
% citation needed here
-- contrary to our first example, we use big-step interpreter and fuel to indicate the operational semantic on an imperative language with side-effect, and we specify the abstract interpretation and prove its soundness, with some of postulation on both computation and property. Then we extend the language feature and we instantiate the postulation on computation for both concrete interpreters and abstract interpreters. Thanks to the compilation, we can directly run the resulting abstract interpreters.

>>>>

\subsection{Abstract Interpreters for Imp}
The second example is adapted and modified from the Familia\citep{zhang2017familia}
-- contrary to our first example, we use big-step interpreter and fuel to indicate the operational semantic on an imperative language with side-effect, and we specify the abstract interpretation and prove its soundness, with some of postulation on both computation and property. Then we extend the language feature and we instantiate the postulation on computation for both concrete interpreters and abstract interpreters. Thanks to the compilation, we can directly run the resulting abstract interpreters.
